Polls of polls to predict the 2024 election

### 2024-11-04 paper/paper.qmd
updated citations

# Overview
The dataset comprises polling data focused on the 2024 U.S. Presidential Election, sourced from prominent aggregators that prioritize transparency and reliability. Each poll is evaluated based on a series of metrics that indicate the quality and methodological rigor of the polling organization. Here, we focus on three key variables that directly assess poll quality: pollscore, transparency_score, and numeric_grade. These variables capture essential aspects of pollster reliability, openness, and methodological rigor, allowing us to assess polling data with precision.
#Measurement
Each variable used in this analysis measures an aspect of poll quality:

@@

# Sample size distribution
```{r, fig.width = 12, fig.height = 6}
#| warning: false
#| message: false
#| echo: false
#| label: fig-ssdistribution
#| fig-cap: "Distribution of Sample Sizes Across Polls: Majority of polls have sample sizes under 5,000, with a few outliers at larger sizes."

@@

### Variation of Poll Quality and Support for Candiates by Pollster

@@

### Support Trend For Candidates

@@

### Variability of Candidate support Across US States

>>>>

Our polling data analysis was conducted using the R programming language [@citeR]. The dataset, sourced from FiveThirtyEight [@fivethirtyeight2024] and encompassing polling data up to November 2, 2024, provides a comprehensive snapshot of public opinion leading into the election. Following the guidelines in @tellingstories, we examined factors affecting voter support percentages, such as poll timing, polling organization characteristics, and regional differences.

To enhance data manipulation, modeling, and visualization, we utilized several R packages. The `tidyverse` package streamlined data wrangling and analysis, improving workflow efficiency [@thereferencecanbewhatever], while the `here` package managed file paths, aiding reproducibility [@citehere]. For data verification, `testthat` was used to confirm that dataset variables were correctly formatted [@citetestthat]. The `knitr` package’s `kable` function allowed for clean table formatting [@citeknitr], and `janitor` supported data cleaning by addressing any dataset quality issues [@citejanitor]. For date manipulation, `lubridate` simplified handling of time variables [@citelubridate], and `arrow` optimized data I/O in parquet format, essential for managing larger datasets [@citearrow]. The `ggplot2` package facilitated data visualization, adding clarity to the analysis [@citeggplot2].

Specialized packages were also used for specific tasks. `modelsummary` enabled efficient reporting of model summaries, streamlining the presentation of regression results [@citemodelsummary], while `RColorBrewer` provided cohesive color palettes to enhance visualization clarity [@citeRColorBrewer]. To improve computational efficiency during model training, we utilized `future` for parallel processing [@citefuture]. For model validation, the `boot` package supported K-Fold cross-validation to assess stability and reliability [@citeboot1;@citeboot2], and `caret` facilitated training and performance evaluation across cross-validation folds [@citecaret]. Our coding structure and file organization were guided by best practices outlined in @tellingstories.

## Overview
The dataset comprises polling data focused on the 2024 U.S. Presidential Election, sourced from prominent aggregators that prioritize transparency and reliability. Each poll is evaluated based on a series of metrics that indicate the quality and methodological rigor of the polling organization. Here, we focus on three key variables that directly assess poll quality: pollscore, transparency_score, and numeric_grade. These variables capture essential aspects of pollster reliability, openness, and methodological rigor, allowing us to assess polling data with precision.
#Measurement
Each variable used in this analysis measures an aspect of poll quality:

@@

## Sample size distribution
```{r, fig.width = 12, fig.height = 6}
#| warning: false
#| message: false
#| echo: false
#| label: fig-ssdistribution
#| fig-cap: "Distribution of Sample Sizes Across Polls: Majority of polls have sample sizes under 5,000, with a few outliers at larger sizes."

@@

##Variation of Poll Quality and Support for Candiates by Pollster

@@

## Support Trend For Candidates

@@

## Variability of Candidate support Across US States
